Distributional Regression Forests for Probabilistic Precipitation Forecasting in Complex Terrain

### 2018-03-09 pkg/disttree/inst/draft/draft.Rnw
small corrections
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2047 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 9784e6640d6cb1bd533d84ac01cdec942cf931d7

In weather forecasting, various factors can make it challenging to 
build a well fitting model. Complex physical processes in the 
atmosphere depend on possibly rapidly changing circumstances. 
Often it is hard to tell which of these circumstances have a 
relevant impact on the quantity of interest and what type of 
effect that can be or how they might interact. A profound 
basis of information can be obtained from numerical weather 
prediction (NWP) models as they provide predictions for a 
large number of meteorological quantities. However, while 
including too many variables in a model can lead to overfitting, 
excluding variables in advance can result in a loss of valuable 
information. Therefore, the task of selecting variables and 
specifying interactions forms the basis of building an adequate 
model. Moreover, this model has to be able to deal with a wide 
range of effects as abrupt changes can appear as well as smooth 
transitions. Especially if the considered region includes complex 
terrain, a large grid spacing of NWP models can lead to abrupt 
local effects within a single NWP grid cell.

As explained in the introduction, distributional forests provide 
a new approach in probabilistic forecasting by embedding the ideas 
of flexible parametric modeling into the framework of tree-structured 
models. The ability to deal with a wide variety of effects and an 
automatic variable selection and detection of interactions are 
features provided by distributional forests that could be particularly 
valuable in probabilistic weather forecasting in order to tackle 
the above mentioned challenges.
To show their strengths in practice, distributional forests are 
now applied to probabilistic precipitation forecasts in a 
mountainous region based on a large number of numerical weather 
prediction quantities. Their results are compared to those of 
other zero-censored Gaussian models including a standard ensemble 
model output approach and two GAMLSS. For one of the GAMLSS the 
regressors have been selected and interactions have been specified 
in advance based on subject-matter knowledge and experience from 
meteorology. The other one is based on a computationally more 
demanding boosting approach.

@@

\item An ensemble model output statistics 
(EMOS, \citealp{Gneiting+Raftery+Westveld:2005}) model where the 
location parameter and the logarithm of the scale parameter depend 
linearly on the ensemble mean forecast of total daily precipitation 
sums and the corresponding ensemble standard deviation respectively.
The choice of the logarithmic function as link function for the scale 
parameter has been made based on the results of 
\cite{Gebetsberger+Messner+Mayr:2017} where different link functions 
have been compared. Moreover, testing the identity, quadratic and 
logarithmic function as link functions in this setting supported 
this choice as the logarithmic function led to the best performance 
of the EMOS model in this application.
\item A GAMLSS where for each distribution parameter the selection 
of covariates and the specification of interactions is done in 
advance, both based on meteorological expert knowledge following 
\cite{Stauffer+Umlauf+Messner:2017} (prespecified GAM). Among the 
available 82 regressors, 9 where selected for the location parameter 
and 6 for the scale parameter. Additionally, for each distribution 
parameter one interaction term is specified in which convective 
available energy is interacting with total precipitation (with the 
ensemble mean for the location parameter and with the ensemble 
standard deviation for the scale parameter). These interactions 
might capture events with a high potential for moderate or severe 
thunderstorms with large amounts of precipitation. By putting 
extra effort in the specification of the formulas the prespecified 
GAM is provided with additional information and is therefore 
expected to profit from this advantage.
\item A boosted GAMLSS \citep{Hofner+Mayr+Schmid:2016} using 
non-homogeneous boosting \citep{Messner+Mayr+Zeileis:2017} 
for an automatic selection of covariates (boosted GAM). 
The idea of this boosting approach is to iteratively minimize 
a loss function where in each step only the coefficient leading 
to the highest improvement of the current model is updated. As 
the initial coefficients are all zero, only the most important 
covariates are included with nonzero coefficients while less 
relevant variables are ignored if the procedure is stopped before 
convergence.
\end{itemize}

%\fixme{Adding a reference to the above paragraph would be good, justifying our knowledge/experience regarding the prespecified GAM. Probably Stauffer+Umlauf+Messner:2017 as I have done in the intro.}

@@

\begin{table}[t!]
\centering
\begin{tabular}{ l l l l }
\hline
Model & Type & Location ($\mu$) & Scale ($\log(\sigma)$) \\
\hline
\textbf{Distributional forest} & recursive    & all & all \\ 
                & partitioning &     &     \\ 
\hline
\textbf{Prespecified GAM} & spline  & \emph{tp{\_}mean}, & \emph{tp{\_}sprd},\\
                            & in each & \emph{tp{\_}max},  & \emph{dswrf{\_}sprd{\_}mean},\\
 & & \emph{tp{\_}mean1218} $\ast$ & \emph{tp{\_}sprd1218} $\ast$\\ 
 & & \quad \emph{cape{\_}mean1218}, & \quad \emph{cape{\_}mean1218},\\
 & & \emph{dswrf{\_}mean{\_}mean}, & \emph{tcolc{\_}sprd{\_}mean},\\
 & & \emph{tcolc{\_}mean{\_}mean}, & \emph{tdiff500850{\_}mean}\\
 & & \emph{pwat{\_}mean{\_}mean}, & \\
 & & \emph{tdiff500850{\_}mean}, & \\
 & & \emph{msl{\_}diff} & \\
\hline
\textbf{Boosted GAM} & spline  & all & all \\
                       & in each &     &     \\
\hline
\textbf{EMOS} & linear & \emph{tp{\_}mean} & \emph{tp{\_}sprd} \\
\hline
\end{tabular}
\caption[Table caption text]{Overview of models with type of 
covariate dependency and included covariates for each distribution 
parameter.}
\label{model_specification}
\end{table}

@@

\subsection{Application for one station}
\label{Application for one station}
First of all we focus on one observation station, Axams in Tyrol. This 
station was selected due to its geographical closeness to Innsbruck, 
the capital of Tyrol. As for all other stations, daily observations and 
numerical weather predictions are available for the month of July of 
28~years from 1985 through the year 2012. In Figure~\ref{axams_onestation} 
the results of fitting a distributional forest to the first 24 years of the 
data set and predicting the total amount of precipitation for one specific 
day of each of the four successive years have been shown as a motivational 
example for a probabilistic forecast. Staying with this fitted model we are 
now going to analyze variable importance of the distributional forest model 
and compare its results to those of the GAMs and the EMOS model based on 
residual QQ-plots.

@@

qqrplot(pit_df_t, nsim = 100, main = "Distributional forest", ylim = c(-5,5), col = gray(0.04, alpha = 0.01), pch = 19)
qqrplot(pit_g_t, nsim = 100, main = "Prespecified GAM", ylim = c(-5,5), col = gray(0.04, alpha = 0.01), pch = 19)
qqrplot(pit_gb_t, nsim = 100, main = "Boosted GAM", ylim = c(-5,5), col = gray(0.04, alpha = 0.01), pch = 19)
qqrplot(pit_ml_t, nsim = 100, main = "EMOS", ylim = c(-5,5), col = gray(0.04, alpha = 0.01), pch = 19)
@
\caption{\label{qqr_oosample} Out-of-sample residual QQ-plots (2009--2012) 
for station Axams based on models learned on data from 1985--2008.}
\end{figure}

After analyzing the results of the models on only one data set where 
visualization is easier, the methods are now going to be evaluated
in a cross validation framework for the station Axams. 
The data set over all 28 years is split into 7 subsets each consisting of 
4 randomly selected years. While 6 of these subsets are used as learning 
data the 7th is the testing data set for which predictions are made and 
evaluated. This is done by calculating the CRPS value for each of the 
observations in the testing data set and then averaging them. Each of the 
7 parts is selected once as testing data which leads to 7 different settings 
of which again the average values are stored. This whole procedure is repeated 
10 times. The resulting skill scores are illustrated in 
Figure~\ref{boxplots_crps_axams} using the EMOS model as the reference model 
represented by the horizontal line at height 0. This CRPS skill score boxplot 
shows that, in this setting, both GAMs and the distributional forest perform 
better than the EMOS model. While the two GAMs lead to an improvement of 
around 4 percent with the boosted version being slightly ahead, the 
distributional forest even reaches an improvement rate close to 6 percent.
<<echo=FALSE, results=hide>>=
#### cross validation rain
if(file.exists("rain_Axams_7x10.rda")){
  load("rain_Axams_7x10.rda")
} else {
  source("rain_cross_7x10.R")
  library("gamlss.cens")
  gen.cens("NO", type = "left")
  rainres <- rain_cross(stationname = "Axams", 
                        seedconst = 7, ntree = 100,
                        forest_mtry = 27,
                        gamboost_cvr = TRUE,
                        frac = FALSE)

@@

\begin{figure}[t!]
\centering
<<rain_cross_axams_crps_skill_score, fig=TRUE, echo=FALSE, height=4.5, width = 6.5>>=
boxplot(1 - rain_crps[,c(2,3,4)] / rain_crps[,6], ylim = c(-0.005, 0.065),
        names = c("Distributional forest", "Prespecified GAM", "Boosted GAM"),
        ylab = "CRPS skill score", col = "lightgray") 
abline(h = 0, col = pal["EMOS"], lwd = 2)
@
\caption{\label{boxplots_crps_axams}CRPS skill score from the 10 times 
7-fold cross validation at station Axams (1985--2012). The horizontal orange 
line pertains to the reference model EMOS.}
\end{figure}

@@

# skill score
s <- 1 - crps_all[, 2:4]/crps_all[,6]
colnames(s) <- c("Distributional forest", "Prespecified GAM", "Boosted GAM")

@@

\begin{figure}[t!]
\centering
<<rain_all_crps_skill_score, fig=TRUE, echo=FALSE, width = 6.5>>=
  matplot(t(s[,]), type = "l", lwd = 2, 
          col = gray(0.5, alpha = 0.2),
          lty = 1, axes = FALSE, 
          xlab = "", ylab = "CRPS skill score", xlim = c(0.5, 3.5))
lines(s[70,], col = "limegreen", type = "o", pch = 19, lwd = 2)  
# Station Axams is the 77th station which is the 70th in the list of complete stations
  boxplot(s, add = TRUE, col = "transparent")
  abline(h = 0, col = pal["EMOS"], lwd = 2)

@@

Figure~\ref{map} shows a map of Tyrol (based on the SRTM 90m Digital Elevation 
Data, \cite{srtm}) with the location of all observation stations included in the 
data set. Each station is illustrated by a symbol with the type of symbol 
representing the method that performed best in terms of CRPS at this station. 
The color of the symbol indicates the difference between the CRPS of the 
distributional forest and the CRPS of the best performing among the other 
three models (prespecified GAM, boosted GAM and EMOS).
Even though for some stations, especially in East Tyrol, one of the two GAMs 
and for a few others the EMOS model leads to the best results, for the 
majority of stations the distributional forest performs best.

@@

  layout(cbind(1, 2), width = c(9, 1))
  par(mar = c(5,4,4,0.1))
  raster::image(tirol.dem, col = rev(gray.colors(100)),
                main="Stations in Tyrol", ylab = "Latitude", xlab = "Longitude", 
                xlim = c(9.8,13.2), 
                ylim = c(46.6, 47.85))
  plot(tirol.gadm, add = TRUE)
  points(sp, pch = c(21, 24, 25, 22)[bst], bg = clr[grp], col = "black", las = 1, cex = 1.5)
  legend(x = 9.8, y = 47.795, pch=c(21,24,25,22), legend = c("Distributional forest", "Prespecified GAM", "Boosted GAM", "EMOS"), cex = 1, bty = "n")
  text(x = 10.3, y = 47.8, labels = "Models with lowest CRPS")
  mtext("CRPS\ndifference", side=4, las = TRUE, at = c(x = 13.5, y = 47.74), line = 0.3)
  par(mar = c(0.5,0.2,0.5,2.3))
  ## legend
  plot(0, 0, type = "n", axes = FALSE, xlab = "", ylab = "",
       xlim = c(0, 1), ylim = c(-0.2, 0.2), xaxs = "i", yaxs = "i")
  rect(0, brk[-6], 0.5, brk[-1], col = rev(clr))
  axis(4, at = brk, las = 1, mgp=c(0,-0.5,-1))

@
\caption{\label{map}Map of Tyrol showing which model performed best at 
which station (type of symbol). The color codes whether the distributional 
forest had lower or higher CRPS (red or blue) compared to the best of the 
other three models (prespecified GAM, boosted GAM and EMOS).}
\end{figure}

@@

\section*{Computational details}
The corresponding implementation to the novel methods presented 
in this article is available on \textsf{R}-Forge in an \textsf{R} 
package called \textbf{disttree} within the project \textbf{partykit} 
(\url{https://R-Forge.R-project.org/projects/partykit/}). The function 
\code{disttree} uses either the \code{mob} or \code{ctree} function 
as a framework to build a tree. Similarly, the function 
\code{distforest} is based on the \code{cforest} function which 
provides a framework to build a distributional forest. All three 
functions, \code{mob}, \code{ctree} and \code{cforest}, are provided 
in the package \textbf{partykit} (\citealt{Hothorn+Zeileis:2015}). 
To specify a distribution family the user can hand over one of the 
following objects as input argument in \code{distfit}, \code{disttree} 
and \code{distforest}: 
\begin{itemize}
\item a GAMLLS family object from the \textsf{R} package \textbf{gamlss} 
(\citealt{Stasinopoulos+Rigby:2007}).
\item a family list generating function from the package \textbf{disttree}.
\item a complete family list from the package \textbf{disttree}.
\item a custom list containing all required information about the 
distribution family.
\end{itemize}

In Section~\ref{ProbabilisticForecasting} the prespecified GAMs were 
built using the function \code{gamlss} from the \textsf{R} package 
\textbf{gamlss.dist} (\citealt{Stasinopoulos+Rigby:2007}). For the 
boosted GAMs the function \code{gamboostLSS} from the \textsf{R} 
package \textbf{gamboostLSS} (\citealt{Hofner+Mayr+Schmid:2016}) 
was applied. The EMOS models were built using the function 
\code{crch} from the \textsf{R} package \textbf{crch} 
(\citealt{Messner+Mayr+Zeileis:2016})

@@

par(mfrow = c(2,2))
pithist(pit_df_t, nsim = 1000, breaks = seq(0, 1, length.out = 9), main = "Distributional forest", ylim = c(0,1.5))
pithist(pit_g_t, nsim = 1000, breaks = seq(0, 1, length.out = 9), main = "Prespecified GAM", ylim = c(0,1.5))
pithist(pit_gb_t, nsim = 1000, breaks = seq(0, 1, length.out = 9), main = "Boosted GAM", ylim = c(0,1.5))
pithist(pit_ml_t, nsim = 1000, breaks = seq(0, 1, length.out = 9), main = "EMOS", ylim = c(0,1.5))

>>>>

In weather forecasting, various factors can make it challenging to 
build a well fitting model. Complex physical processes in the 
atmosphere depend on possibly rapidly changing circumstances. 
Often it is hard to tell which of these circumstances have a 
relevant impact on the quantity of interest and what type of 
effect that can be or how they might interact. A profound 
basis of information can be obtained from numerical weather 
prediction (NWP) models as they provide predictions for a 
large number of meteorological quantities. However, while 
including too many variables in a model can lead to overfitting, 
excluding variables in advance can result in a loss of valuable 
information. Therefore, the task of selecting variables and 
specifying interactions forms the basis of building an adequate 
model. Moreover, this model has to be able to deal with a wide 
range of effects as abrupt changes can appear as well as smooth 
transitions. Especially if the considered region includes complex 
terrain, a large grid spacing of NWP models can lead to abrupt 
local effects within a single grid cell.

As explained in the introduction, distributional forests provide 
a new approach in probabilistic forecasting by embedding the ideas 
of flexible parametric modeling into the framework of tree-structured 
models. In that way, they offer features that could be particularly 
valuable in probabilistic weather forecasting in order to tackle 
the above mentioned challenges. Among these features are the ability 
to deal with a wide variety of effects and an automatic variable 
selection and detection of interactions. 
To show their strengths in practice, distributional forests are 
now applied to probabilistic precipitation forecasts in a 
mountainous region based on a large number of numerical weather 
prediction quantities. Their results are compared to those of 
other zero-censored Gaussian models including a standard ensemble 
model output approach and two GAMLSS. For one of the GAMLSS the 
regressors have been selected and interactions have been specified 
in advance based on subject-matter knowledge and experience from 
meteorology. The other one is based on a computationally more 
demanding boosting approach.

@@

\item Ensemble model output statistics 
(EMOS, \citealp{Gneiting+Raftery+Westveld:2005}): The 
location parameter and the logarithm of the scale parameter depend 
linearly on the ensemble mean forecast of total daily precipitation 
sums and the corresponding ensemble standard deviation respectively.
The choice of the logarithmic function as link function for the scale 
parameter has been made based on the results of 
\cite{Gebetsberger+Messner+Mayr:2017} where different link functions 
have been compared. Moreover, testing the identity, quadratic and 
logarithmic function as link functions in this setting supported 
this choice as the logarithmic function led to the best performance 
of the EMOS model in this application.
\item Prespecified GAMLSS: For each distribution parameter the selection 
of covariates and the specification of interactions is done in 
advance, both based on meteorological expert knowledge following 
\cite{Stauffer+Umlauf+Messner:2017}. Among the 
available 82 regressors, 9 are selected for the location parameter 
and 6 for the scale parameter. Additionally, for each distribution 
parameter one interaction term is specified in which convective 
available energy is interacting with total precipitation (with the 
ensemble mean for the location parameter and with the ensemble 
standard deviation for the scale parameter). These interactions 
might capture events with a high potential for moderate or severe 
thunderstorms with large amounts of precipitation. By putting 
extra effort in the specification of the formulas the prespecified 
GAM is provided with additional information and is therefore 
expected to profit from this advantage.
\item Boosted GAMLSS: Non-homogeneous boosting 
\citep{Messner+Mayr+Zeileis:2017} is used for an automatic 
selection of covariates \citep{Hofner+Mayr+Schmid:2016}. 
The idea of this boosting approach is to iteratively minimize 
a loss function where in each step only the coefficient leading 
to the highest improvement of the current model is updated. As 
the initial coefficients are all zero, only the most important 
covariates are included with nonzero coefficients while less 
relevant variables are ignored if the procedure is stopped before 
convergence.
\end{itemize}

%\fixme{Adding a reference to the above paragraph would be good, justifying our knowledge/experience regarding the prespecified GAMLSS. Probably Stauffer+Umlauf+Messner:2017 as I have done in the intro.}

@@

\begin{table}[t!]
\centering
\begin{tabular}{ l l l l }
\hline
Model & Type & Location ($\mu$) & Scale ($\log(\sigma)$) \\
\hline
\textbf{Distributional forest} & recursive    & all & all \\ 
                & partitioning &     &     \\ 
\hline
\textbf{Prespecified GAMLSS} & spline  & \emph{tp{\_}mean}, & \emph{tp{\_}sprd},\\
                            & in each & \emph{tp{\_}max},  & \emph{dswrf{\_}sprd{\_}mean},\\
 & & \emph{tp{\_}mean1218} $\ast$ & \emph{tp{\_}sprd1218} $\ast$\\ 
 & & \quad \emph{cape{\_}mean1218}, & \quad \emph{cape{\_}mean1218},\\
 & & \emph{dswrf{\_}mean{\_}mean}, & \emph{tcolc{\_}sprd{\_}mean},\\
 & & \emph{tcolc{\_}mean{\_}mean}, & \emph{tdiff500850{\_}mean}\\
 & & \emph{pwat{\_}mean{\_}mean}, & \\
 & & \emph{tdiff500850{\_}mean}, & \\
 & & \emph{msl{\_}diff} & \\
\hline
\textbf{Boosted GAMLSS} & spline  & all & all \\
                       & in each &     &     \\
\hline
\textbf{EMOS} & linear & \emph{tp{\_}mean} & \emph{tp{\_}sprd} \\
\hline
\end{tabular}
\caption[Table caption text]{Overview of models with type of 
covariate dependency and included covariates for each distribution 
parameter.}
\label{model_specification}
\end{table}

@@

\subsection{Application for one station}
\label{Application for one station}
First of all we focus on one observation station, Axams in Tyrol. This 
station is selected due to its geographical closeness to Innsbruck, 
the capital of Tyrol. As for all other stations, daily observations and 
numerical weather predictions are available for the month of July of 
28~years from 1985 through the year 2012. In Figure~\ref{axams_onestation} 
the results of fitting a distributional forest to the first 24 years of the 
data set and predicting the total amount of precipitation for one specific 
day of each of the four successive years have been shown as a motivational 
example for a probabilistic forecast. Staying with this fitted model we are 
now going to analyze variable importance of the distributional forest model 
and compare its results to those of the prespecified and the boosted GAMLSS 
and the EMOS model based on residual QQ-plots.

@@

qqrplot(pit_df_t, nsim = 100, main = "Distributional forest", ylim = c(-5,5), col = gray(0.04, alpha = 0.01), pch = 19)
qqrplot(pit_g_t, nsim = 100, main = "Prespecified GAMLSS", ylim = c(-5,5), col = gray(0.04, alpha = 0.01), pch = 19)
qqrplot(pit_gb_t, nsim = 100, main = "Boosted GAMLSS", ylim = c(-5,5), col = gray(0.04, alpha = 0.01), pch = 19)
qqrplot(pit_ml_t, nsim = 100, main = "EMOS", ylim = c(-5,5), col = gray(0.04, alpha = 0.01), pch = 19)
@
\caption{\label{qqr_oosample} Out-of-sample residual QQ-plots (2009--2012) 
for station Axams based on models learned on data from 1985--2008.}
\end{figure}

After analyzing the results of the models on only one data set where 
visualization is easier, the methods are now going to be evaluated
in a cross validation framework for the station Axams. 
The data set over all 28 years is split into 7 subsets each consisting of 
4 randomly selected years. While 6 of these subsets are used as learning 
data the 7th is the testing data set for which predictions are made and 
evaluated. This is done by calculating the CRPS value for each of the 
observations in the testing data set and then averaging them. Each of the 
7 parts is selected once as testing data which leads to 7 different settings 
of which again the average values are stored. This whole procedure is repeated 
10 times. The resulting skill scores are illustrated in 
Figure~\ref{boxplots_crps_axams} using the EMOS model as the reference model 
represented by the horizontal line at height 0. This CRPS skill score boxplot 
shows that, in this setting, both GAMLSS and the distributional forest perform 
better than the EMOS model. While the two GAMLSS lead to an improvement of 
around 4 percent with the boosted version being slightly ahead, the 
distributional forest even reaches an improvement rate close to 6 percent.
<<echo=FALSE, results=hide>>=
#### cross validation rain
if(file.exists("rain_Axams_7x10.rda")){
  load("rain_Axams_7x10.rda")
} else {
  source("rain_cross_7x10.R")
  library("gamlss.cens")
  gen.cens("NO", type = "left")
  rainres <- rain_cross(stationname = "Axams", 
                        seedconst = 7, ntree = 100,
                        forest_mtry = 27,
                        gamboost_cvr = TRUE,
                        frac = FALSE)

@@

\begin{figure}[t!]
\centering
<<rain_cross_axams_crps_skill_score, fig=TRUE, echo=FALSE, height=4.5, width = 7>>=
boxplot(1 - rain_crps[,c(2,3,4)] / rain_crps[,6], ylim = c(-0.005, 0.065),
        names = c("Distributional forest", "Prespecified GAMLSS", "Boosted GAMLSS"),
        ylab = "CRPS skill score", col = "lightgray") 
abline(h = 0, col = pal["EMOS"], lwd = 2)
@
\caption{\label{boxplots_crps_axams}CRPS skill score from the 10 times 
7-fold cross validation at station Axams (1985--2012). The horizontal orange 
line pertains to the reference model EMOS.}
\end{figure}

@@

# skill score
s <- 1 - crps_all[, 2:4]/crps_all[,6]
colnames(s) <- c("Distributional forest", "Prespecified GAMLSS", "Boosted GAMLSS")

@@

\begin{figure}[t!]
\centering
<<rain_all_crps_skill_score, fig=TRUE, echo=FALSE, width = 7>>=
  matplot(t(s[,]), type = "l", lwd = 2, 
          col = gray(0.5, alpha = 0.2),
          lty = 1, axes = FALSE, 
          xlab = "", ylab = "CRPS skill score", xlim = c(0.5, 3.5))
lines(s[70,], col = "limegreen", type = "o", pch = 19, lwd = 2)  
# Station Axams is the 77th station which is the 70th in the list of complete stations
  boxplot(s, add = TRUE, col = "transparent")
  abline(h = 0, col = pal["EMOS"], lwd = 2)

@@

Figure~\ref{map} shows a map of Tyrol (based on the SRTM 90m Digital Elevation 
Data, \cite{srtm}) with the location of all observation stations included in the 
data set. Each station is illustrated by a symbol with the type of symbol 
representing the method that performed best in terms of CRPS at this station. 
The color of the symbol indicates the difference between the CRPS of the 
distributional forest and the CRPS of the best performing among the other 
three models (prespecified GAMLSS, boosted GAMLSS and EMOS).
Even though for some stations, especially in East Tyrol, one of the two GAMLSS 
and for a few others the EMOS model leads to the best results, for the 
majority of stations the distributional forest performs best.

@@

  layout(cbind(1, 2), width = c(9, 1))
  par(mar = c(5,4,4,0.1))
  raster::image(tirol.dem, col = rev(gray.colors(100)),
                main="Stations in Tyrol", ylab = "Latitude", xlab = "Longitude", 
                xlim = c(9.8,13.2), 
                ylim = c(46.6, 47.87))
  plot(tirol.gadm, add = TRUE)
  points(sp, pch = c(21, 24, 25, 22)[bst], bg = clr[grp], col = "black", las = 1, cex = 1.5)
  legend(x = 9.8, y = 47.815, pch=c(21,24,25,22), legend = c("Distributional forest", "Prespecified GAMLSS", "Boosted GAMLSS", "EMOS"), cex = 1, bty = "n")
  text(x = 10.3, y = 47.82, labels = "Models with lowest CRPS")
  mtext("CRPS\ndifference", side=4, las = TRUE, at = c(x = 13.5, y = 47.76), line = 0.3)
  par(mar = c(0.5,0.2,0.5,2.3))
  ## legend
  plot(0, 0, type = "n", axes = FALSE, xlab = "", ylab = "",
       xlim = c(0, 1), ylim = c(-0.2, 0.2), xaxs = "i", yaxs = "i")
  rect(0, brk[-6], 0.5, brk[-1], col = rev(clr))
  axis(4, at = brk, las = 1, mgp=c(0,-0.5,-1))

@
\caption{\label{map}Map of Tyrol showing which model performed best at 
which station (type of symbol). The color codes whether the distributional 
forest had lower or higher CRPS (red or blue) compared to the best of the 
other three models (prespecified GAMLSS, boosted GAMLSS and EMOS).}
\end{figure}

@@

\section*{Computational details}
The corresponding implementation to the novel methods presented 
in this article is available on \textsf{R}-Forge in an \textsf{R} 
package called \textbf{disttree} within the project \textbf{partykit} 
(\url{https://R-Forge.R-project.org/projects/partykit/}). The function
\code{distfit} fits a distributional model and is called within the
tree-building function \code{disttree} and the forest-building
function \code{distforest}. 
Within \code{disttree} either the \code{mob} or \code{ctree} function 
can be applied as a framework to build a tree. Similarly, the function 
\code{distforest} is based on the function \code{cforest}. All three 
functions, \code{mob}, \code{ctree} and \code{cforest}, are provided 
in the package \textbf{partykit} (\citealt{Hothorn+Zeileis:2015}). 
To specify a distribution family the user can hand over one of the 
following objects as input argument in \code{distfit}, \code{disttree} 
and \code{distforest}: 
\begin{itemize}
\item a GAMLLS family object from the \textsf{R} package \textbf{gamlss.dist} 
(\citealt{Stasinopoulos+Rigby:2007}).
\item a family list generating function from the package \textbf{disttree}.
\item a complete family list from the package \textbf{disttree}.
\item a custom list containing all required information about the 
distribution family.
\end{itemize}

In Section~\ref{ProbabilisticForecasting} the prespecified GAMLSS were 
built using the function \code{gamlss} from the \textsf{R} package 
\textbf{gamlss} (\citealt{Stasinopoulos+Rigby:2007}). For the 
boosted GAMLSS the function \code{gamboostLSS} from the \textsf{R} 
package \textbf{gamboostLSS} (\citealt{Hofner+Mayr+Schmid:2016}) 
was applied. The EMOS models were built using the function 
\code{crch} from the \textsf{R} package \textbf{crch} 
(\citealt{Messner+Mayr+Zeileis:2016})

@@

par(mfrow = c(2,2))
pithist(pit_df_t, nsim = 1000, breaks = seq(0, 1, length.out = 9), main = "Distributional forest", ylim = c(0,1.5))
pithist(pit_g_t, nsim = 1000, breaks = seq(0, 1, length.out = 9), main = "Prespecified GAMLSS", ylim = c(0,1.5))
pithist(pit_gb_t, nsim = 1000, breaks = seq(0, 1, length.out = 9), main = "Boosted GAMLSS", ylim = c(0,1.5))
pithist(pit_ml_t, nsim = 1000, breaks = seq(0, 1, length.out = 9), main = "EMOS", ylim = c(0,1.5))
